---
title: "lec11"
author: "Marika Fong"
date: "2022-11-02"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
```

```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
#dot plot of percollege vs peradultpoverty showing the trend line
plot <- ggplot(data = midwest) +
  geom_hex(mapping = aes(
    x = percollege,
    y = percadultpoverty
  ), color = "green") +
    geom_smooth(mapping = aes(
      x = percollege,
      y = percadultpoverty
    ))
plot


#creating an aesthetic mapping for x and y-axis
point_mapping <- aes(x = midwest$percollege, y = midwest$percadultpoverty)
point_mapping

#using aestheric mapping to create points 
points <- geom_point(mapping = point_mapping)

# adds points to the plot
plot <- plot + points


#wrangling data
by_state <- midwest %>% 
  group_by(state) %>% 
  summarize(pop_total = sum(poptotal))
by_state

#bar chart
plot <- ggplot(data = by_state) +
  geom_col(
    mapping = aes(
    x = state,
    y = pop_total
  ))
plot

#making the chart blue
plot3 <- ggplot(data = by_state) +
  geom_col(
    mapping = aes(
    x = state,
    y = pop_total
  ),
fill = "lightblue"
) + 
  scale_y_continuous(labels = scales :: comma) +
  labs(
    x = "State",
    y = "Population",
    title = "Population Figures for Midwest States",
    subtitle = "Data from ggplot2() midwest data frame.",
    caption = "Lecture 11 exercise.",
    alt = "Population Figures for Midwest Stats"
  )
plot3

```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
